Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1,t2}

### 2024-02-08 article/OLD.qmd
s
s

[^10]: There are two possible reasons that may explain the differences in the GLS standard errors. On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).

>>>>

[^10]: There are two possible reasons that may explain the differences in the GLS standard errors. On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-ifs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).

### 2024-02-08 article/alt_article.qmd
s
s

---
title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1,t2}
author:
  - name: Fernando Rios-Avila
    email: friosavi@levy.org
    affiliations: 
        - id: levy
          name: Levy Economics Institute of Bard College
          city: Annandale-on-Hudson, NY
          country: USA          
    attributes:
        corresponding: true
  - name: Leonardo Siles
    email: leonardo.siles@ucb.edu.bo
    affiliations:
        - id: ucb
          name: Universidad Católica Boliviana
          city: La Paz
          country: Bolivia
  - name: Gustavo Canavire-Bacarreza
    email: gcanavire@worldbank.org
    affiliations:
        - id: wb
          name: The World Bank                 
          city: Washington, D.C.
          country: USA
abstract: |
  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for the estimation of standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP, allowing for both time and country fixed effects.

@@

date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      formatting: review
      model: 1p
      cite-style: authoryear
      number-depth: 2
include-in-header: 
      text: |
        \tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}    
        \tnotetext[t2]{The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.}

@@

-->

@@

[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).

>>>>

---
title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments 
author:
  - name: Fernando Rios-Avila
    email: friosavi@levy.org
    affiliations: 
        - id: levy
          name: Levy Economics Institute of Bard College
          city: Annandale-on-Hudson, NY
          country: USA

  - name: Leonardo Siles
    email: leonardo.siles@ucb.edu.bo
    affiliations:
        - id: ucb
          name: Universidad Católica Boliviana
          city: La Paz
          country: Bolivia
  - name: Gustavo Canavire-Bacarreza
    email: gcanavire@worldbank.org
    affiliations:
        - id: wb
          name: The World Bank                 
          city: Washington, D.C.
          country: USA
abstract: |
  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for the estimation of standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP, allowing for both time and country fixed effects.

@@

date: last-modified
bibliography: bibliography.bib
format:
  pdf: 
    toc-depth: 2
    number-sections: true
    documentclass: article
    margin-bottom: 1in
    margin-top: 1in
    margin-left: 1in
    margin-right: 1in
    thanks: |
      The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.

      The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.

    fontsize: 11pt
    cite-method: natbib

@@

-->
{{< pagebreak >}}

@@

[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see #eq-ifs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).

### 2024-02-08 article/article.tex
s
s

Considering the estimated effects across quantiles, we observe few
differences in the reported GLS standard errors compared to the
analytical standard errors reported in MSS. Our clustered standard
errors, however, are closer to the bootstrap-based standard errors the
authors report.\footnote{The differences in the GLS standard errors may
  be due that in our derivation the influence function of the
  standardized \(\tau_{th}\) quantile (see \#eq-infs) does not have the
  same leading term as the one reported in MSS (see Theorem 3, and the
  definition of \(W\)).}

>>>>

Considering the estimated effects across quantiles, we observe few
differences in the reported GLS standard errors compared to the
analytical standard errors reported in MSS. Our clustered standard
errors, however, are closer to the bootstrap-based standard errors the
authors report.\footnote{The differences in the GLS standard errors may
  be due that in our derivation the influence function of the
  standardized \(\tau_{th}\) quantile (see \#eq-ifs) does not have the
  same leading term as the one reported in MSS (see Theorem 3, and the
  definition of \(W\)).}
